\bf Title here

### 2020-07-20 paper/paper.Rmd
add math for data simulation and reference to tidy data

[I would add the maths here to describe the simulations. ppp]

Two set of simulated data are used in the demo of the visual diagnostics in projection pursuit guided tour. A small dataset consists of 1000 randomly simulated observations of five variables (`x1`, `x2`, `x8`, `x9`, `x10`). `x2` is the informative variable simulated from two bi-modal normal distribution centred at -3 and 3 with variance of one and the other four are simulated from non-informative standard random normal distributions. The data has been scaled to ensure `x2` has variance of 1. The goal is to find the 1D projection of bi-modal shape, which corresponds to the projection matrix (vector) of `[0, 1, 0, 0, 0]`.

A larger dataset contains more informative variables (`x3` to `x7`) of different types. The distribution of all the variables except `x3` is plotted in Figure \ref{origin-data} and `x3` takes 500 positive one and 500 negative one. [should I introduce the dist for each var? xxx] [also feel like we don't really use `x3` to `x6`, should we not mention about these? xxx]

@@

In tour, when the optimisation ends the global object will be stored and printed and can be turned off via `print = FALSE`. Additional messages during the optimisation can be displayed via `verbose = TRUE`. Below presented the global object of the 1D projection using the small dataset. [the printing is not ideal as it doesn't show all the columns. xxx]

```{r code, eval = FALSE}
set.seed(123456)
holes_1d_geo <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_geodesic),
                  rescale = FALSE, verbose = TRUE)

@@

```{r glb-obj-1}
holes_1d_geo %>% head(5)
```

>>>>

We first simulate some random variables of size 1000 with different structures. `x1`, `x8`, `x9` and `x10` are simulated from normal distribution iwth zero mean and variance of one as in equation \ref{eq:sim-norm}. When using projection pursuit to explore the data structure based on its departure from normality, the entry in the projection basis for these variables should be close to zero in theory. `x2` to `x7` are mixture of normal distribution with different weights and locations. Equation \ref{eq:sim-x2} to \ref{eq:sim-x7} show the distribution of each variables and Figure \ref{origin-data} shows the histogram of each variable except `x3`. All the variables are then scaled to ensure the mixture has variance of one.

\begin{align}
x_1 \overset{d}{=} x_8 \overset{d}{=} x_9 \overset{d}{=} x_{10}& \sim \mathcal{N}(0, 1) \label{eq:sim-norm} \\
x_2 &\sim 0.5 \mathcal{N}(-3, 1) + 0.5 \mathcal{N}(3, 1)\label{eq:sim-x2}\\
\Pr(x_3) &= 
\begin{cases}
0.5 & \text{if $x_3 = -1$ or $1$}\\
0 & \text{otherwise}
\end{cases}\label{eq:sim-x3}\\
x_4 &\sim 0.25 \mathcal{N}(-3, 1) + 0.75 \mathcal{N}(3, 1) \label{eq:sim-x4}\\
x_5 &\sim \frac{1}{3} \mathcal{N}(-5, 1) + \frac{1}{3} \mathcal{N}(0, 1) + \frac{1}{3} \mathcal{N}(5, 1)\label{eq:sim-x5}\\
x_6 &\sim 0.45 \mathcal{N}(-5, 1) + 0.1 \mathcal{N}(0, 1) + 0.45 \mathcal{N}(5, 1)\label{eq:sim-x6}\\
x_7 &\sim 0.5 \mathcal{N}(-5, 1) + 0.5 \mathcal{N}(5, 1) 
\label{eq:sim-x7}
\end{align}

@@

We form our first dataset using variable `x1`, `x2`, `x8`, `x9` and `x10` and supply it to one of the above algorithm, say `search_geodesic` in the `tourr` package. When the optimisation ends, the global object will be stored and printed (it can be turned off by supplying argument `print = FALSE`). Additional messages during the optimisation can be displayed by `verbose = TRUE`. Below shows the first five rows of the global object. The global object meets the definition of tidy data introduced in [@wickham2014tidy] where each observation forms a row, each variable forms a column and each type of observational unit forms a table. The adoption of tidy data makes it easier for data wrangling and visualisation, which powers the visual diagnostics system introduced in this paper.

```{r code, eval = FALSE}
set.seed(123456)
holes_1d_better <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_better),
                  rescale = FALSE, verbose = TRUE)

@@

```{r glb-obj-1}
print(holes_1d_better %>% head(5))
```

### 2020-07-20 paper/paper.tex
add math for data simulation and reference to tidy data

{[}I would add the maths here to describe the simulations. ppp{]}

Two set of simulated data are used in the demo of the visual diagnostics
in projection pursuit guided tour. A small dataset consists of 1000
randomly simulated observations of five variables (\texttt{x1},
\texttt{x2}, \texttt{x8}, \texttt{x9}, \texttt{x10}). \texttt{x2} is the
informative variable simulated from two bi-modal normal distribution
centred at -3 and 3 with variance of one and the other four are
simulated from non-informative standard random normal distributions. The
data has been scaled to ensure \texttt{x2} has variance of 1. The goal
is to find the 1D projection of bi-modal shape, which corresponds to the
projection matrix (vector) of \texttt{{[}0,\ 1,\ 0,\ 0,\ 0{]}}.

A larger dataset contains more informative variables (\texttt{x3} to
\texttt{x7}) of different types. The distribution of all the variables
except \texttt{x3} is plotted in Figure \ref{origin-data} and
\texttt{x3} takes 500 positive one and 500 negative one. {[}should I
introduce the dist for each var? xxx{]} {[}also feel like we don't
really use \texttt{x3} to \texttt{x6}, should we not mention about
these? xxx{]}

@@

In tour, when the optimisation ends the global object will be stored and
printed and can be turned off via \texttt{print\ =\ FALSE}. Additional
messages during the optimisation can be displayed via
\texttt{verbose\ =\ TRUE}. Below presented the global object of the 1D
projection using the small dataset. {[}the printing is not ideal as it
doesn't show all the columns. xxx{]}

\begin{verbatim}
## # A tibble: 5 x 8
##   basis           index_val tries info            loop method        alpha    id
##   <list>              <dbl> <dbl> <chr>          <dbl> <chr>         <dbl> <int>
## 1 <dbl[,1] [5 x ~     0.749     1 start             NA <NA>            0.5     1
## 2 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       2
## 3 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       3
## 4 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       4
## 5 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       5
\end{verbatim}

>>>>

We first simulate some random variables of size 1000 with different
structures. \texttt{x1}, \texttt{x8}, \texttt{x9} and \texttt{x10} are
simulated from normal distribution iwth zero mean and variance of one as
in equation \ref{eq:sim-norm}. When using projection pursuit to explore
the data structure based on its departure from normality, the entry in
the projection basis for these variables should be close to zero in
theory. \texttt{x2} to \texttt{x7} are mixture of normal distribution
with different weights and locations. Equation \ref{eq:sim-x2} to
\ref{eq:sim-x7} show the distribution of each variables and Figure
\ref{origin-data} shows the histogram of each variable except
\texttt{x3}. All the variables are then scaled to ensure the mixture has
variance of one.

\begin{align}
x_1 \overset{d}{=} x_8 \overset{d}{=} x_9 \overset{d}{=} x_{10}& \sim \mathcal{N}(0, 1) \label{eq:sim-norm} \\
x_2 &\sim 0.5 \mathcal{N}(-3, 1) + 0.5 \mathcal{N}(3, 1)\label{eq:sim-x2}\\
\Pr(x_3) &= 
\begin{cases}
0.5 & \text{if $x_3 = -1$ or $1$}\\
0 & \text{otherwise}
\end{cases}\label{eq:sim-x3}\\
x_4 &\sim 0.25 \mathcal{N}(-3, 1) + 0.75 \mathcal{N}(3, 1) \label{eq:sim-x4}\\
x_5 &\sim \frac{1}{3} \mathcal{N}(-5, 1) + \frac{1}{3} \mathcal{N}(0, 1) + \frac{1}{3} \mathcal{N}(5, 1)\label{eq:sim-x5}\\
x_6 &\sim 0.45 \mathcal{N}(-5, 1) + 0.1 \mathcal{N}(0, 1) + 0.45 \mathcal{N}(5, 1)\label{eq:sim-x6}\\
x_7 &\sim 0.5 \mathcal{N}(-5, 1) + 0.5 \mathcal{N}(5, 1) 
\label{eq:sim-x7}
\end{align}

@@

We form our first dataset using variable \texttt{x1}, \texttt{x2},
\texttt{x8}, \texttt{x9} and \texttt{x10} and supply it to one of the
above algorithm, say \texttt{search\_geodesic} in the \texttt{tourr}
package. When the optimisation ends, the global object will be stored
and printed (it can be turned off by supplying argument
\texttt{print\ =\ FALSE}). Additional messages during the optimisation
can be displayed by \texttt{verbose\ =\ TRUE}. Below shows the first
five rows of the global object. The global object meets the definition
of tidy data introduced in \citep{wickham2014tidy} where each
observation forms a row, each variable forms a column and each type of
observational unit forms a table. The adoption of tidy data makes it
easier for data wrangling and visualisation, which powers the visual
diagnostics system introduced in this paper.

\begin{verbatim}
## # A tibble: 5 x 8
##   basis             index_val tries info           loop method       alpha    id
##   <list>                <dbl> <dbl> <chr>         <dbl> <chr>        <dbl> <int>
## 1 <dbl[,1] [5 x 1]>     0.749     1 start            NA <NA>           0.5     1
## 2 <dbl[,1] [5 x 1]>     0.730     1 random_search     1 search_bett~   0.5     2
## 3 <dbl[,1] [5 x 1]>     0.743     1 random_search     2 search_bett~   0.5     3
## 4 <dbl[,1] [5 x 1]>     0.736     1 random_search     3 search_bett~   0.5     4
## 5 <dbl[,1] [5 x 1]>     0.747     1 random_search     4 search_bett~   0.5     5
\end{verbatim}
